---
title: "Chicago Bulls Analysis"
author: "Jingjing Tang"
date: "2023-05-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
# load libraries
library(tidyverse)
library(ggplot2)
```

## 1. Introduction

This section should provide relevant background information and justification for the project, including:

a)  relevant background information of basketball, including key metrics, position requirements etc

b)  description of the scenario

c)  the aim of the project

d)  justification and importance

## 2. Reading and cleaning the raw data 

#### Load data into R

In this section, all 5 datasets are imported into R. 

-   `2018-19_nba_player-salaries.csv` includes the salary information of individual players in the NBA for the 2018-19 season. It is saved in the dataframe called `salary`.
-   `2018-19_nba_player-statistics.csv` provides comprehensive statistical information for each NBA player throughout the 2018-19 season. It is saved in the dataframe called `player_stats`.
-   `2018-19_nba_team-statistics_1.csv` includes various team statistics for in the NBA for the 2018-19 season. It is saved in the dataframe called `team_stat_1`.
-   `2018-19_nba_team-statistics_2.csv` includes comprehensive team statistics for the NBA's 2018-19 season. It is saved in the dataframe called `team_stat_2`.
-   `2019-20_nba_team-payroll.csv`includes the team's budget for payroll during the 2019-20 NBA season. It is saved in the dataframe called `payroll`.

More details of these datasets, which includes variables descriptions, can be found through [the link](https://uclearn.canberra.edu.au/courses/13262/pages/data-description-reproducible-data-analysis-project).

```{r data, echo=TRUE}
salary <- read.csv("project-data/raw/2018-19_nba_player-salaries.csv")
player_stats <- read.csv("project-data/raw/2018-19_nba_player-statistics.csv")
team_stat_1 <- read.csv("project-data/raw/2018-19_nba_team-statistics_1.csv")
team_stat_2 <- read.csv("project-data/raw/2018-19_nba_team-statistics_2.csv")
payroll <- read.csv("project-data/raw/2019-20_nba_team-payroll.csv")
```

#### Understand data

In this section, each code chunk will check the structure of the data frames, and check the summary information of the data frames.

-   salary

    `salary` contains 576 observations and 3 variables. There is no missing values in this dataframe.

```{r}
str(salary)
summary(salary)
```

-   player_stats

    `player_stats` dataframe contains 708 observations and 29 variables. This dataframe has NA values in 4 variables: FG., X3P., X2P., eFG..

```{r}
str(player_stats)
summary(player_stats)
```

-   team_stat_1

    `team_stat_1` dataframe contains 30 observations and 25 variables. 3 columns with missing values were found, which does not contain any data.

```{r}
str(team_stat_1)
summary(team_stat_1)
```

-   team_stat_2

    `team_stat_2` dataframe contains 30 observations and 25 variables. No missing values were found in this dataframe.

```{r}
str(team_stat_2)
summary(team_stat_2)
```

-   payroll

    `payroll` dataframe contains 30 observations and 3 variables. No missing values were found in this dataframe.

```{r}
str(payroll)
summary(payroll)
```

#### Clean data

As mentioned before, variables contains 100% NA values should be removed in team_stat_1.

```{r}
team_stat_1 <- team_stat_1[, -which(apply(team_stat_1, 2, function(x) all(is.na(x))))]
```

Variable salary in payroll should be numeric instead of character. Hence, \$ and , signs should be removed from the variable.

```{r include=FALSE}
payroll$salary <- gsub("\\$", "", payroll$salary)
payroll$salary <- gsub(",", "", payroll$salary)
payroll$salary <- as.numeric(payroll$salary, na.rm=TRUE)
class(payroll$salary)
```

#### Combine data

Player statistics play a crucial role in determining the optimal starting lineup. However, calculating the total payroll for the upcoming season is impossible without salary information. Therefore, we will only consider players present in the salary data frame.

```{r}
#combine player stats data and salary data
players <- right_join(salary, player_stats, by="player_name")
#remove players without salary information
players <- players[complete.cases(players$salary), ]
```

```{r}
#save players dataframe into csv
write.csv(players, "project-data/processed/players.csv", row.names = FALSE)
```

## 3. Exploratory analysis

This section should document your exploratory data analysis and may include but is not limited to:

a)  checking for errors and missing values within the datasets

b)  checking the distribution of variables

c)  checking for relationships between variables, or differences between groups

d)  justification for decisions made about data modelling

#### Data Visualisation

The first plot aim to investigate the distribution of the salaries across the whole league in each position in 2018-19 NBA season. This box plot illustrates that *centers* may be more expensive, as they have the highest average salary. At the same time, *point guards* have the widest distribution of salaries and the most expensive players, but their average salary is the lowest among all positions.

```{r}
#boxplot of salary in each positions
p1 <- players %>%
  filter(Pos %in% c("PG", "SG", "SF", "PF", "C")) %>%
  ggplot(aes(x=Pos, y=salary)) +
  geom_boxplot() +
  labs(x="Position", y="Salary", 
       title="Salary among different positions in 2018-19 NBA season") +
  theme_classic()
p1
```

```{r include=FALSE}
# store the graph into figs folder
ggsave("figs/salary-among-pos.png", p1)
```

In order to optimize the cost associated with a trade, it is necessary to conduct a thorough investigation of the current squad and have a better understanding of the current team.

According to the data below, there are 20 players listed as Chicago Bulls players. This exceeds the limitation of 15 players on its roster. Additionally, the player with the highest salary on the roster is Otto Porter, who earns \$26,011,913. He plays in the small forward position.

```{r}
#count the current roaster number
player_chi <- players %>%
  filter(Tm %in% c("CHI")) %>%
  filter(Pos %in% c("PG", "SG", "SF", "PF", "C"))
paste0("Currently there are ",count(player_chi), " players in Chicago Bulls roaster.")

temp_index <- grep(max(player_chi$salary), player_chi$salary)
max_name <- player_chi[temp_index,]$player_name
max_salary <- player_chi[temp_index,]$salary
max_pos <- player_chi[temp_index,]$Pos
paste0("The most expensive player on the roaster is ", max_name, " with a salary of ", max_salary, ". His position is ", max_pos, ".")

```

#### Relationships between variables

-   Point Guard

```{r}
# corration
```

Shooting Guard

```{r}

```

Small Forward

```{r}

```

Power Forward

```{r}

```

Center

```{r}

```

## 4. Data modelling and results

This section may include but is not limited to:

a)  data modelling (e.g. creating a linear regression)

b)  assumption checking

c)  model output and interpretation of your model

\

## 5. Player recommendations

**This section will be the key part that is presented to the general manager**. Here you should present your recommendations for the best five starting players, but also think about what other important information they would want to know, and how it is best to present that information to them.  

## 6. Summary

Provide a brief summary which describes the key points and findings from your project. It will also be important to acknowledge any limitations of your model and overall approach to answering the question asked of you by the general manager.

\

## 7. Reference list
