---
title: "Chicago Bulls Analysis"
author: "Jingjing Tang"
date: "2023-05-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Introduction

This section should provide relevant background information and justification for the project, including:

a)  relevant background information of basketball, including key metrics, position requirements etc

b)  description of the scenario

c)  the aim of the project

d)  justification and importance

## 2. Reading and cleaning the raw data 

**Load data into R**\
In this section, all 5 datasets are imported into R. 

-   `2018-19_nba_player-salaries.csv` includes the salary information of individual players in the NBA for the 2018-19 season. It is saved in the dataframe called `salary`.
-   `2018-19_nba_player-statistics.csv` provides comprehensive statistical information for each NBA player throughout the 2018-19 season. It is saved in the dataframe called `player_stats`.
-   `2018-19_nba_team-statistics_1.csv` includes various team statistics for in the NBA for the 2018-19 season. It is saved in the dataframe called `team_stat_1`.
-   `2018-19_nba_team-statistics_2.csv` includes comprehensive team statistics for the NBA's 2018-19 season. It is saved in the dataframe called `team_stat_2`.
-   `2019-20_nba_team-payroll.csv`includes the team's budget for payroll during the 2019-20 NBA season. It is saved in the dataframe called `payroll`.

More details of these datasets, which includes variables descriptions, can be found through [the link](https://uclearn.canberra.edu.au/courses/13262/pages/data-description-reproducible-data-analysis-project).

```{r data, echo=TRUE}
salary <- read.csv("project-data/raw/2018-19_nba_player-salaries.csv")
player_stats <- read.csv("project-data/raw/2018-19_nba_player-statistics.csv")
team_stat_1 <- read.csv("project-data/raw/2018-19_nba_team-statistics_1.csv")
team_stat_2 <- read.csv("project-data/raw/2018-19_nba_team-statistics_2.csv")
payroll <- read.csv("project-data/raw/2019-20_nba_team-payroll.csv")
```

**Check data**

In this section, each code chunk will check the structure of the data frames, and check the summary information of the data frames.

-   salary

```{r}
str(salary)
summary(salary)
```

-   player_stats

```{r}
str(player_stats)
summary(player_stats)
```

-   team_stat_1

```{r}
str(team_stat_1)
summary(team_stat_1)
```

-   team_stat_2

```{r}
str(team_stat_2)
summary(team_stat_2)
```

-   payroll

```{r}
str(payroll)
summary(payroll)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## 3. Exploratory analysis

This section should document your exploratory data analysis and may include but is not limited to:

a)  checking for errors and missing values within the datasets

b)  checking the distribution of variables

c)  checking for relationships between variables, or differences between groups

d)  justification for decisions made about data modelling

## 4. Data modelling and results

This section may include but is not limited to:

a)  data modelling (e.g. creating a linear regression)

b)  assumption checking

c)  model output and interpretation of your model

\

## 5. Player recommendations

**This section will be the key part that is presented to the general manager**. Here you should present your recommendations for the best five starting players, but also think about what other important information they would want to know, and how it is best to present that information to them.  

## 6. Summary

Provide a brief summary which describes the key points and findings from your project. It will also be important to acknowledge any limitations of your model and overall approach to answering the question asked of you by the general manager.

\

## 7. Reference list
