---
title: "Chicago Bulls Analysis"
author: "Jingjing Tang"
date: "2023-05-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
# load libraries
library(tidyverse)
library(ggplot2)
library(broom)
```

## 1. Introduction

#### Scenario

As a data analyst for the Chicago Bulls in the NBA, the task at hand is to find the best five starting players within the team's budget of \$118 million for the upcoming 2019-20 season. The team's poor performance in the previous season, ranking 27th out of 30 based on win-loss record, makes this task particularly important. Additionally, Chicago Bulls team budget ranks 26th out of 30, with the highest payroll budget, Portland, having \$148 million and the best-performing team, Milwaukee Bucks, having a payroll budget of \$131 million in the previous season.

#### Relevant background of basketball

The team, Chicago Bulls are a professional basketball team based in Chicago and they compete in the NBA (National Basketball Association), which is the premier professional basketball league in North America and one of the most popular and prestigious basketball leagues in the world. Chicago Bulls ranked 27th out of 30 during 2018-19 season, which is not an ideal result.

In basketball, there are five positions on a team: point guard, shooting guard, small forward, power forward, and center. The following list outlines each position and its specific roles and responsibilities.

1.  Point Guard (PG): The point guard is usually the team's primary ball-handler and playmaker. They are responsible for bringing the ball up the court, setting up offensive plays, and distributing the ball to their teammates. A good point guard is often characterised by their assists (number of passes leading directly to a basket), steals (number of times they take the ball from an opposing player), turnovers and their ability to be a scoring threat (3-points percentages)$^{1}$.

2.  Shooting Guard (SG): The shooting guard's primary role is to score points by shooting the ball from the outside and driving to the basket. A good shooting guard is often characterised by their shooting percentages (field goal percentage, three-point percentage, free throw percentage, effective field goal percentage).

3.  Small Forward (SF): The small forward is a all-around position that requires a combination of skills, including shooting and defending. They often play a role as a secondary ball handler and are required to have good dribbling skills. A good small forward is often characterised by their all-around statistics, including shooting percentages (2-points percentage), rebounds, and steals$^{2}$.

4.  Power Forward (PF): The power forward is typically the most physical and aggressive player who plays close to the basket. They are responsible for securing rebounds and keeping possession. Therefore, a good power forward is often characterised by their defensive statistics (Offensive Rebounds, Defensive Rebounds, Blocks)$^{3}$.

5.  Center (C): The center is typically the tallest player on the team and plays close to the basket. They are responsible for defending the basket, scoring points in the paint, blocking shots, and grabbing rebounds. A good center is often characterised by their rebounding (total rebounds), blocks and shooting percentage (2-points percentage).

The maximum roster size in the NBA is 15 players, with a minimum of 13 players required during the regular season. Each team should have 5 players on the court during a game and an additional 8 players available on the bench. This means 12 of the players on the roster can be active on a game day, while the remaining 3 players on the roster are typically inactive and serve as backups in case of injury or other emergencies$^{4}$.

#### Project aim

The project aims to use data analysis and visualization techniques to identify players across the NBA league, that can provide the highest value for Chicago Bulls within the salary cap. Ultimately, the goal of this project is to enhance the team's performance and future success in the upcoming season.

#### Justification and importance

The importance of this project lies in its ability to provide data-driven insights and decision makings for player selection that can positively impact the team's overall performance and success. This project should also assist with optimise the team's budget and ensure that the funds are utilised properly.

## 2. Reading and cleaning the raw data 

#### Load data into R

In this section, all 5 datasets are imported into R. 

-   `2018-19_nba_player-salaries.csv` includes the salary information of individual players in the NBA for the 2018-19 season. It is saved in the dataframe called `salary`.
-   `2018-19_nba_player-statistics.csv` provides comprehensive statistical information for each NBA player throughout the 2018-19 season. It is saved in the dataframe called `player_stats`.
-   `2018-19_nba_team-statistics_1.csv` includes various team statistics for in the NBA for the 2018-19 season. It is saved in the dataframe called `team_stat_1`.
-   `2018-19_nba_team-statistics_2.csv` includes comprehensive team statistics for the NBA's 2018-19 season. It is saved in the dataframe called `team_stat_2`.
-   `2019-20_nba_team-payroll.csv`includes the team's budget for payroll during the 2019-20 NBA season. It is saved in the dataframe called `payroll`.

More details of these datasets, which includes variables descriptions, can be found through [the link](https://uclearn.canberra.edu.au/courses/13262/pages/data-description-reproducible-data-analysis-project).

```{r data, echo=TRUE}
salary <- read.csv("project-data/raw/2018-19_nba_player-salaries.csv")
player_stats <- read.csv("project-data/raw/2018-19_nba_player-statistics.csv")
team_stat_1 <- read.csv("project-data/raw/2018-19_nba_team-statistics_1.csv")
team_stat_2 <- read.csv("project-data/raw/2018-19_nba_team-statistics_2.csv")
payroll <- read.csv("project-data/raw/2019-20_nba_team-payroll.csv")
```

#### Understand data

In this section, each code chunk will check the structure of the data frames, and check the summary information of the data frames.

-   salary

    `salary` contains 576 observations and 3 variables. There is no missing values in this dataframe.

```{r}
str(salary)
summary(salary)
```

-   player_stats

    `player_stats` dataframe contains 708 observations and 29 variables. This dataframe has NA values in 4 variables: FG., X3P., X2P., eFG..

```{r}
str(player_stats)
summary(player_stats)
```

-   team_stat_1

    `team_stat_1` dataframe contains 30 observations and 25 variables. 3 columns with missing values were found, which does not contain any data.

```{r}
str(team_stat_1)
summary(team_stat_1)
```

-   team_stat_2

    `team_stat_2` dataframe contains 30 observations and 25 variables. No missing values were found in this dataframe.

```{r}
str(team_stat_2)
summary(team_stat_2)
```

-   payroll

    `payroll` dataframe contains 30 observations and 3 variables. No missing values were found in this dataframe.

```{r}
str(payroll)
summary(payroll)
```

#### Clean data

As mentioned before, variables contains 100% NA values should be removed in team_stat_1.

```{r}
team_stat_1 <- team_stat_1[, -which(apply(team_stat_1, 2, function(x) all(is.na(x))))]
```

Variable salary in payroll should be numeric instead of character. Hence, \$ and , signs should be removed from the variable.

```{r include=FALSE}
payroll$salary <- gsub("\\$", "", payroll$salary)
payroll$salary <- gsub(",", "", payroll$salary)
payroll$salary <- as.numeric(payroll$salary, na.rm=TRUE)
class(payroll$salary)
```

#### Combine data

Player statistics play a crucial role in determining the optimal starting lineup. However, calculating the total payroll for the upcoming season is impossible without salary information. Therefore, we will only consider players present in the salary data frame.

```{r}
#combine player stats data and salary data
players <- right_join(salary, player_stats, by="player_name")
#remove players without salary information
players <- players[complete.cases(players$salary), ]
```

```{r}
#save players dataframe into csv
write.csv(players, "project-data/processed/players.csv", row.names = FALSE)
```

## 3. Exploratory analysis

#### Data Visualisation

The first plot aim to investigate the distribution of the salaries across the whole league in each position in 2018-19 NBA season. This box plot illustrates that *centers* may be more expensive, as they have the highest average salary. At the same time, *point guards* have the widest distribution of salaries and the most expensive players, but their average salary is the lowest among all positions.

```{r}
#boxplot of salary in each positions
p1 <- players %>%
  filter(Pos %in% c("PG", "SG", "SF", "PF", "C")) %>%
  ggplot(aes(x=Pos, y=salary)) +
  geom_boxplot() +
  labs(x="Position", y="Salary", 
       title="Salary among different positions in 2018-19 NBA season") +
  theme_classic()
p1
```

```{r include=FALSE}
# store the graph into figs folder
ggsave("figs/salary-among-pos.png", p1)
```

In order to optimize the cost associated with a trade, it is necessary to conduct a thorough investigation of the current squad and have a better understanding of the current team.

According to the data below, there are 20 players listed as Chicago Bulls players. This exceeds the limitation of 15 players on its roster. Additionally, the player with the highest salary on the roster is Otto Porter, who earns \$26,011,913. He plays in the small forward position. In this case, Otto is not performing impressive data like his salary, so he could be cut from the current team. Meanwhile, Zach LaVine is the highest playing time on court, which means he is the current star player for Chicago Bulls.

```{r}
#count the current roaster number
player_chi <- players %>%
  filter(Tm %in% c("CHI")) %>%
  filter(Pos %in% c("PG", "SG", "SF", "PF", "C"))
paste0("Currently there are ",count(player_chi), " players in Chicago Bulls roaster.")

temp_index <- grep(max(player_chi$salary), player_chi$salary)
max_name <- player_chi[temp_index,]$player_name
max_salary <- player_chi[temp_index,]$salary
max_pos <- player_chi[temp_index,]$Pos
paste0("The most expensive player on the roaster is ", max_name, " with a salary of ", max_salary, ". His position is ", max_pos, ".")

temp_index <- grep(max(player_chi$MP), player_chi$MP)
max_time_name <- player_chi[temp_index,]$player_name
paste0("The player with the most minutes played is ", max_time_name, ".")

```

#### Relationships between variables

This section will explore the relationship between the variables chose and explained in the introduction for each position. It shall help to identify potential causal relationships between variables, to develop better models and make better predictions.

-   Point Guard

    Assists (AST), steals (STL), turnovers (TOV), 3-points percentages (X3P.) are considered as key indicators for assessing point guard's performance and effectiveness. A high number of assists indicates that the point guard is effectively creating scoring opportunities for their teammates. A high number of steals and turnovers indicates that the point guard has excellent abilities to disrupt the opposing team's offensive flow and lead to scoring opportunities. A high 3-point percentage indicates that the point guard is a skilled long-range shooter and effectively winning points from the perimeter.

```{r}
# filter all point guard players and make a new df
pg <- players %>%
  filter(Pos %in% "PG")

# plot relationships
pairs(formula = ~salary + AST + STL + TOV + `X3P.`, data=pg)
```

Based on the plot, it appears that there is some degree of association between salary and the chosen variables. Furthermore, assists, steals, and turnovers demonstrate a strong correlation, which is likely due to their significance in evaluating a point guard's performance. It is possible that players who struggle in one area may struggle in others as well.

-   Shooting Guard

    Field goal percentage (FG.), three-point percentage (X3P.), free throw percentage (FT.), effective field goal percentage (eFG.) are identified as important metrics to measure the ability of a shooting guard. All the chosen variables are related to goal winning percentage, which means the shooting guard is able to consistently make shots.

```{r}
# filter all shooting guard players and make a new df
sg <- players %>%
  filter(Pos %in% "SG")

# plot relationships
pairs(formula = ~salary + FG. + X3P. + FT. + eFG., data=sg)
```

According to this plot, there appears to be no significant correlation between salary and selected variables as indicated by the flat slope. Additionally, a few outliers are identified. Meanwhile, effective field goal percentage has a weak relationship to field goal percentage and 3-point goal percentage, as it is calculated from these statistics.

-   Small Forward

    Two-points field goal percentage (X2P.), total rebounds (TRB), and steals (STL) are essential to measuring small forwars. Small forwards are expected to score from inside the paint and mid-range areas, creating 2-point field goals, hence, 2-point percentage is an important indicator to reflect their scoring efficiency and effectiveness. Meanwhile, as a all-round player on the court, small forward should contribute on both offense and defense, therefore, a high total rebounds and steals indicates that the player is active and engaged in the game, which leads to team success.

```{r}
# filter all small forward players and make a new df
sf <- players %>%
  filter(Pos %in% "SF")

# plot relationships
pairs(formula = ~salary + X2P. + TRB + STL, data=sf)
```

Based on the plot, the salary is positively correlate to the selected variables. Meanwhile, total rebounds and steals are positively relate to each other. It might because both total rebounds and steals require a strong defensive skill set, hence, good players who perform well in one of these areas are likely to excel in the other.

-   Power Forward

    Offensive rebounds (ORB), defensive rebounds (DRB), blocks (BLK) are important indicators of a power forward's effectiveness on the court. Offensive rebounds indicate a power forward's ability to grab a missed shot by their team and give them another chance to score, while defensive rebounds show their ability to prevent the opposing team from getting an offensive rebound and creating more scoring opportunities. Additionally, blocks are an important statistic for power forwards because they demonstrate the ability to defend the rim and protect the basket from scoring attempts by the opposing team. These data reflects a power forward's defensive ability, which is critical to assess the effectiveness of a power forward on the court.

```{r}
# filter all power forward players and make a new df
pf <- players %>%
  filter(Pos %in% "PF")

# plot relationships
pairs(formula = ~salary + ORB + DRB + BLK, data=pf)
```

The plot demonstrate the relationship between each variables. It is evident that there is a positive correlation between salary, offensive rebounds (ORB), defensive rebounds (DRB), and blocks (BLK). It is crucial to note that a strong correlation between predictors can negatively affect the model's performance. Hence, the model should be proceed carefully with the issue of multicollinearity.

-   Center

    Total rebounds (TRB), blocks (BLK) and 2-points goal percentage (X2P.) are identified as key measurements for center players. A high total rebounds number and blocks indicates that the player can control the paint and good at defending the basket. Additionally, centers typcally score points in the paint by dunking, layups, or hook shots, therefore, the center's ability to score efficiently from inside the paint is reflected in their two-point field goal percentage.

```{r}
# filter all center players and make a new df
cc <- players %>%
  filter(Pos %in% "C")

# plot relationships
pairs(formula = ~salary + TRB + BLK + X2P., data=cc)

```

The plot provides an insightful view of the relationship between the variables salary, total rebounds (TRB), blocks (BLK) and 2-points goal percentage (X2P.). As stated previously, TRB and BLK are highly correlated, as they both measure a player's defensive capabilities. A player who excels in defensive performance is likely to receive a higher salary. Additionally, the plot reveals some outliers, particularly in the relationship between salary and 2-points goal percentage.

## 4. Data modelling and results

This section will build models for each position, evaluate assumptions and analyse the results.

#### Point Guard

```{r}
# build model for point guard
model_pg <- lm(salary ~ AST + STL + TOV + `X3P.`, data=pg)
tidy(model_pg, conf.int=TRUE)
```

The linear regression model was built based on the response variable salary and predict variables assist (AST), steals (STL), turnovers (TOV) and 3-point field goal percentage (X3P.). This model provides the equation: `salary = 1635137.63 + 12179.31 * AST + 27508.10 * STL + 25865.68 * TOV - 271069.47 * X3P.`

Although this is unlikely to happen in real life in a team, the model indicates that even with 0 assist, 0 steals, 0 turnovers, and 0 three-point field goal percentage, a point guard player could still receive a minimum salary of 1,635,137.63 dollars. Additionally, for every additional unit of AST, salary is estimated to increase by \$12,179.31, holding all other predictors constant. Similar to other predict variables. It is also worth mention that the P-value for selected variables are not significant (higher than 0.05), which indicates statistically these variables do not have a significant impact on determining a point guard's salary.

```{r}
# check variance inflation factor
sqrt(car::vif(model_pg))

#none with a VIF value above 5
```

```{r}
# predict salary for pg
pg <- mutate(pg, exp_salary = predict(model_pg, newdata=pg))
```

```{r warning=FALSE}
# plot the predicted value against actual value
ggplot(pg, aes(x=exp_salary, y=salary)) + 
  geom_point() +
  geom_abline(linetype="dashed", colour="red")
```

#### Shooting Guard

```{r}
# build model for shooting guard
model_sg <- lm(salary ~ FG. + X3P. + FT. + eFG., data=sg)
tidy(model_sg, conf.int=TRUE)
```

The linear regression model was built based on the response variable salary and predict variables field goals (FG), 3-point field goal percentage (X3P.), free throw (FT), effective field goal percentage (eFG). This model provides the equation: `salary = -3297710 + 36856597 * FG + 9498467 * X3P + 6840098 * FT - 28110171 * eFG.`

The model indicates that with 0 field goals, 0 3-point field goal percentage, 0 free throw, and 0 effective field goal percentage, a shooting guard player could not receive any salary. Meanwhile, for every additional unit of FG, salary is estimated to increase by \$`36,856,597`, holding all other predictors constant. Similar to other predict variables. It is also worth mention that the P-value for selected variables are not significant (higher than 0.05), which indicates statistically these variables do not have a significant impact on determining a shooting guard's salary.

```{r}
# check variance inflation factor
sqrt(car::vif(model_sg))

#none with a VIF value above 5
```

```{r}
# predict salary for sg
sg <- mutate(sg, exp_salary = predict(model_sg, newdata=sg))
```

```{r warning=FALSE}
# plot the predicted value against actual value
ggplot(sg, aes(x=exp_salary, y=salary)) + 
  geom_point() +
  geom_abline(linetype="dashed", colour="red")
```

#### Small Forward

```{r}
# build model for small forward
model_sf <- lm(salary ~ X2P. + TRB + STL, data=sf)
tidy(model_sf, conf.int=TRUE)
```

The linear regression model was built based on the response variable salary and predict variables 2-points goal percentage (X2P.), total rebounds (TRB) and steals (STL). This model provides the equation: `salary = 4270006.42 - 6119055.25 * X2P + 21120.79 * TRB + 64035.38 * STL.`

The model indicates that with 0 two-points goal percentage, 0 total rebounds and 0 steal, a small forward player could receive a minimum salary of \$`4,270,006.42`. Meanwhile, for every additional unit of X2P, salary is estimated to decrease by \$`6,119,055.25`, holding all other predictors constant. Similar to other predict variables. It is also worth mention that the P-value for selected variables are not significant (higher than 0.05), which indicates statistically these variables do not have a significant impact on determining a small forward's salary.

```{r}
# check variance inflation factor
sqrt(car::vif(model_sf))

#none with a VIF value above 5
```

```{r}
# predict salary for sf
sf <- mutate(sf, exp_salary = predict(model_sf, newdata=sf))
```

```{r warning=FALSE}
# plot the predicted value against actual value
ggplot(sf, aes(x=exp_salary, y=salary)) + 
  geom_point() +
  geom_abline(linetype="dashed", colour="red")
```

#### Power Forward

```{r}
# build model for power forward
model_pf <- lm(salary ~ ORB + DRB + BLK, data=pf)
tidy(model_pf, conf.int=TRUE)
```

The linear regression model was built based on the response variable salary and predict variables offensive rebounds (ORB), defensive rebounds (DRB) and blocks (BLK). This model provides the equation: `salary = 2523692.24 - 25836.84 * ORB + 34776.27 * DRB - 30824.06 * BLK.`

The model indicates that with 0 offensive rebounds, 0 defensive rebounds and 0 blocks, a power forward player could receive a minimum salary of \$`2,523,692.24`. Meanwhile, for every additional unit of ORB, salary is estimated to decrease by \$`25,836.84`, which is not necessary in the real world. Similar to other predict variables. It is also worth mention that the P-value for selected variables are significant (lower than 0.05), which indicates statistically these variables have a significant impact on determining a power forward's salary.

```{r}
# check variance inflation factor
sqrt(car::vif(model_pf))

#none with a VIF value above 5
```

```{r}
# predict salary for pf
pf <- mutate(pf, exp_salary = predict(model_pf, newdata=pf))
```

```{r}
# plot the predicted value against actual value
ggplot(pf, aes(x=exp_salary, y=salary)) + 
  geom_point() +
  geom_abline(linetype="dashed", colour="red")
```

#### Center

```{r}
# build model for power forward
model_cc <- lm(salary ~ TRB + BLK + X2P., data=cc)
tidy(model_cc, conf.int=TRUE)
```

The linear regression model was built based on the response variable salary and predict variables total rebounds (TRB), blocks (BLK), and 2-points goal percentage (X2P.). This model provides the equation: `salary = 4654588.68 + 19394.64 * TRB - 40863.48 * BLK + 454056.68 * X2P.`

The model indicates that with 0 total rebounds, 0 dblocks and 0 2-points goal percentage, a center player could receive a minimum salary of \$`4,654,588.68`. It is also worth mention that the P-value for selected variables are significant (lower than 0.05), which indicates statistically these variables have a significant impact on determining a center's salary.

```{r}
# check variance inflation factor
sqrt(car::vif(model_cc))

#none with a VIF value above 5
```

```{r}
# predict salary for center
cc <- mutate(cc, exp_salary = predict(model_cc, newdata=cc))
```

```{r}
# plot the predicted value against actual value
ggplot(cc, aes(x=exp_salary, y=salary)) + 
  geom_point() +
  geom_abline(linetype="dashed", colour="red")
```

#### Assumptions

The response variable `salary` is continuous because it can take on any value within a range. All the predict variables are continuous, as they are either ratio or interval scale. The observations of players across the NBA league are independent of each other. As tested before, there are linear relationships between salary and each explanatory variable. There appear to be some outliers or high leverage points in the data; however, it is possible to provide justifiable reasons for their presence. According to the variance inflation factor values, calculated in each section, none of them were above 5, which means there is no significant multicollinearity.\

## 5. Player recommendations

**Point guard**

```{r}
# point guard 
pg %>%
  select(player_name, exp_salary, salary, Age, Tm, MP, PTS) %>%
  arrange(exp_salary) %>%
  top_n(20)
```

James Harden could be Chicago Bulls next starting point guard. He is currently playing in Houston Rockets, with the highest total points win on the list. The expected salary for him is \$23,028,756, and his current salary is \$30,570,000. Harden is a famous player in the NBA, known for his signature step-back jump shot. This could bring experience to the team. On the other hand, youngsters such as Jamal Murray, Trae Young should be recruited, as they have the potential to shoot or create chances for the team. Jamal Murray has an expected salary at \$11,886,564, but his current salary is \$3,499,800; similarly, Trae Young has an expected salary at \$19,447,612, but his current salary is \$5,363,280.

```{r}
# save the recommendation players in a new df
recommendation <- pg %>%
filter(player_name %in% c("James Harden", "Jamal Murray", "Trae Young"))
```

**Shooting guard**

```{r}
# shooting guard 
sg %>%
  select(player_name, exp_salary, salary, Age, Tm, MP, PTS) %>%
  arrange(exp_salary) %>%
  top_n(20)
```

Donovan Mitchell could be the starting shooting guard for the next season, while considering Buddy Hield, Devin Booker as bench players. Donovan Mitchell is a young player who is currently plays for Utah Jazz. Mitchell is a shooting guard with a relevantly high total points, which makes him one of the most promising young stars in the NBA. He shall have an expected salary at \$7,717,589, however, his current salary is at \$3,111,480. Similarly, Buddy Hield and Devin Booker are also young players who have demonstrated promising statistics and command a relatively low salary. This makes them ideal candidates for recruitment as bench players.

```{r}
temp_df <- sg %>%
filter(player_name %in% c("Donovan Mitchell", "Buddy Hield", "Devin Booker"))
recommendation <- rbind(recommendation, temp_df)
```

**Small forward**

```{r}
# small forward 
sf %>%
  select(player_name, exp_salary, salary, Age, Tm, MP, PTS) %>%
  arrange(exp_salary) %>%
  top_n(20)
```

Bojan Bogdanovic shall be picked as the starting 5 players for Chicago Bulls, while Brandon Ingram and Jayson Tatum shall serve as bench players.

```{r}
temp_df <- sf %>%
  filter(player_name %in% c("Bojan Bogdanovic", "Chicago Bulls", "Brandon Ingram"))
recommendation <- rbind(recommendation, temp_df)
```

**Power forward**

```{r}

```

Center

```{r}

```

## 6. Summary

Provide a brief summary which describes the key points and findings from your project. It will also be important to acknowledge any limitations of your model and overall approach to answering the question asked of you by the general manager.

#### Limitation

While this model can provide valuable insights into potential valuable players for the next season and provide ideas for how teams should approach signings, it is important to acknowledge that the model still has limitations. One of the limitations is the presence of outliers in the data. For instance, some players may have high salaries despite poor performance. This could be due to insufficient data collected, as some players may have missed games due to injuries. This could negatively affect the accuracy of the prediction. Furthermore, some players may have mediocre data, but possess outstanding skills that may be beneficial to a team. However, such skills may not be noticeable in the model. This could lead to missed opportunities for teams to acquire players that are a good fit for their needs. Moreover, signing players may come with additional expenses such as associate fees, which could cause a team's budget to be insufficient. This may limit their ability to acquire the best players available. Finally, team tactics are not always fixed. The tactics of a new season may not align with the team's tactics at the time of signings, which could result in players not performing well after being signed. This could lead to significant losses for the team. Therefore, it is important for teams to carefully consider all factors before making any signings based solely on the model's predictions.

#### Conclusion

\

## 7. Reference list

1.  Haefner J. 7 ways to make a better point guard [Internet]. 2011 [cited 2023 May 7]. Available from: <https://www.usab.com/youth/news/2011/06/7ways-to-make-a-better-point-guard.aspx#:~:text=Point%20guard%20is%20perhaps%20the,against%20the%20opposing%20point%20guard.>

2.  The ultimate guide to playing small forward [Internet]. 2015 [cited 2023 May 8]. Available from: <https://www.usab.com/youth/news/2011/06/the-ultimate-guide-to-playing-small-forward.aspx>

3.  The ultimate guide to playing power forward [Internet]. 2015 [cited 2023 May 8]. Available from: <https://www.usab.com/youth/news/2011/06/the-ultimate-guide-to-playing-power-forward.aspx>

4.  How many players on a basketball team? (roster size) [Internet]. 2023 [cited 2023 May 8]. Available from: <https://www.gaimday.com/blog/players-basketball-team/>
