---
title: "Chicago Bulls Analysis"
author: "Jingjing Tang"
date: "2023-05-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
# load libraries
library(tidyverse)
library(ggplot2)
```

## 1. Introduction

#### Scenario

As a data analyst for the Chicago Bulls in the NBA, the task at hand is to find the best five starting players within the team's budget of \$118 million for the upcoming 2019-20 season. The team's poor performance in the previous season, ranking 27th out of 30 based on win-loss record, makes this task particularly important. Additionally, Chicago Bulls team budget ranks 26th out of 30, with the highest payroll budget, Portland, having \$148 million and the best-performing team, Milwaukee Bucks, having a payroll budget of \$131 million in the previous season.

#### Relevant background of basketball

The team, Chicago Bulls are a professional basketball team based in Chicago and they compete in the NBA (National Basketball Association), which is the premier professional basketball league in North America and one of the most popular and prestigious basketball leagues in the world. Chicago Bulls ranked 27th out of 30 during 2018-19 season, which is not an ideal result.

In basketball, there are five positions on a team: point guard, shooting guard, small forward, power forward, and center. The following list outlines each position and its specific roles and responsibilities.

1.  Point Guard (PG): The point guard is usually the team's primary ball-handler and playmaker. They are responsible for bringing the ball up the court, setting up offensive plays, and distributing the ball to their teammates. A good point guard is often characterised by their assists (number of passes leading directly to a basket), steals (number of times they take the ball from an opposing player), turnovers and their ability to be a scoring threat (3-points percentages)$^{1}$.

2.  Shooting Guard (SG): The shooting guard's primary role is to score points by shooting the ball from the outside and driving to the basket. A good shooting guard is often characterised by their shooting percentages (field goal percentage, three-point percentage, free throw percentage, effective field goal percentage).

3.  Small Forward (SF): The small forward is a all-around position that requires a combination of skills, including shooting and defending. They often play a role as a secondary ball handler and are required to have good dribbling skills. A good small forward is often characterised by their all-around statistics, including shooting percentages (2-points percentage), rebounds, and steals$^{2}$.

4.  Power Forward (PF): The power forward is typically the most physical and aggressive player who plays close to the basket. They are responsible for securing rebounds and keeping possession. Therefore, a good power forward is often characterised by their defensive statistics (Offensive Rebounds, Defensive Rebounds, Blocks)$^{3}$.

5.  Center (C): The center is typically the tallest player on the team and plays close to the basket. They are responsible for defending the basket, scoring points in the paint, blocking shots, and grabbing rebounds. A good center is often characterised by their rebounding (total rebounds), blocks and shooting percentage (2-points percentage).

The maximum roster size in the NBA is 15 players, with a minimum of 13 players required during the regular season. Each team should have 5 players on the court during a game and an additional 8 players available on the bench. This means 12 of the players on the roster can be active on a game day, while the remaining 3 players on the roster are typically inactive and serve as backups in case of injury or other emergencies$^{4}$.

#### Project aim

The project aims to use data analysis and visualization techniques to identify players across the NBA league, that can provide the highest value for Chicago Bulls within the salary cap. Ultimately, the goal of this project is to enhance the team's performance and future success in the upcoming season.

#### Justification and importance

The importance of this project lies in its ability to provide data-driven insights and decision makings for player selection that can positively impact the team's overall performance and success. This project should also assist with optimise the team's budget and ensure that the funds are utilised properly.

## 2. Reading and cleaning the raw data 

#### Load data into R

In this section, all 5 datasets are imported into R. 

-   `2018-19_nba_player-salaries.csv` includes the salary information of individual players in the NBA for the 2018-19 season. It is saved in the dataframe called `salary`.
-   `2018-19_nba_player-statistics.csv` provides comprehensive statistical information for each NBA player throughout the 2018-19 season. It is saved in the dataframe called `player_stats`.
-   `2018-19_nba_team-statistics_1.csv` includes various team statistics for in the NBA for the 2018-19 season. It is saved in the dataframe called `team_stat_1`.
-   `2018-19_nba_team-statistics_2.csv` includes comprehensive team statistics for the NBA's 2018-19 season. It is saved in the dataframe called `team_stat_2`.
-   `2019-20_nba_team-payroll.csv`includes the team's budget for payroll during the 2019-20 NBA season. It is saved in the dataframe called `payroll`.

More details of these datasets, which includes variables descriptions, can be found through [the link](https://uclearn.canberra.edu.au/courses/13262/pages/data-description-reproducible-data-analysis-project).

```{r data, echo=TRUE}
salary <- read.csv("project-data/raw/2018-19_nba_player-salaries.csv")
player_stats <- read.csv("project-data/raw/2018-19_nba_player-statistics.csv")
team_stat_1 <- read.csv("project-data/raw/2018-19_nba_team-statistics_1.csv")
team_stat_2 <- read.csv("project-data/raw/2018-19_nba_team-statistics_2.csv")
payroll <- read.csv("project-data/raw/2019-20_nba_team-payroll.csv")
```

#### Understand data

In this section, each code chunk will check the structure of the data frames, and check the summary information of the data frames.

-   salary

    `salary` contains 576 observations and 3 variables. There is no missing values in this dataframe.

```{r}
str(salary)
summary(salary)
```

-   player_stats

    `player_stats` dataframe contains 708 observations and 29 variables. This dataframe has NA values in 4 variables: FG., X3P., X2P., eFG..

```{r}
str(player_stats)
summary(player_stats)
```

-   team_stat_1

    `team_stat_1` dataframe contains 30 observations and 25 variables. 3 columns with missing values were found, which does not contain any data.

```{r}
str(team_stat_1)
summary(team_stat_1)
```

-   team_stat_2

    `team_stat_2` dataframe contains 30 observations and 25 variables. No missing values were found in this dataframe.

```{r}
str(team_stat_2)
summary(team_stat_2)
```

-   payroll

    `payroll` dataframe contains 30 observations and 3 variables. No missing values were found in this dataframe.

```{r}
str(payroll)
summary(payroll)
```

#### Clean data

As mentioned before, variables contains 100% NA values should be removed in team_stat_1.

```{r}
team_stat_1 <- team_stat_1[, -which(apply(team_stat_1, 2, function(x) all(is.na(x))))]
```

Variable salary in payroll should be numeric instead of character. Hence, \$ and , signs should be removed from the variable.

```{r include=FALSE}
payroll$salary <- gsub("\\$", "", payroll$salary)
payroll$salary <- gsub(",", "", payroll$salary)
payroll$salary <- as.numeric(payroll$salary, na.rm=TRUE)
class(payroll$salary)
```

#### Combine data

Player statistics play a crucial role in determining the optimal starting lineup. However, calculating the total payroll for the upcoming season is impossible without salary information. Therefore, we will only consider players present in the salary data frame.

```{r}
#combine player stats data and salary data
players <- right_join(salary, player_stats, by="player_name")
#remove players without salary information
players <- players[complete.cases(players$salary), ]
```

```{r}
#save players dataframe into csv
write.csv(players, "project-data/processed/players.csv", row.names = FALSE)
```

## 3. Exploratory analysis

This section should document your exploratory data analysis and may include but is not limited to:

a)  checking for errors and missing values within the datasets

b)  checking the distribution of variables

c)  checking for relationships between variables, or differences between groups

d)  justification for decisions made about data modelling

#### Data Visualisation

The first plot aim to investigate the distribution of the salaries across the whole league in each position in 2018-19 NBA season. This box plot illustrates that *centers* may be more expensive, as they have the highest average salary. At the same time, *point guards* have the widest distribution of salaries and the most expensive players, but their average salary is the lowest among all positions.

```{r}
#boxplot of salary in each positions
p1 <- players %>%
  filter(Pos %in% c("PG", "SG", "SF", "PF", "C")) %>%
  ggplot(aes(x=Pos, y=salary)) +
  geom_boxplot() +
  labs(x="Position", y="Salary", 
       title="Salary among different positions in 2018-19 NBA season") +
  theme_classic()
p1
```

```{r include=FALSE}
# store the graph into figs folder
ggsave("figs/salary-among-pos.png", p1)
```

In order to optimize the cost associated with a trade, it is necessary to conduct a thorough investigation of the current squad and have a better understanding of the current team.

According to the data below, there are 20 players listed as Chicago Bulls players. This exceeds the limitation of 15 players on its roster. Additionally, the player with the highest salary on the roster is Otto Porter, who earns \$26,011,913. He plays in the small forward position. Meanwhile, Zach LaVine is the highest playing time on court.

```{r}
#count the current roaster number
player_chi <- players %>%
  filter(Tm %in% c("CHI")) %>%
  filter(Pos %in% c("PG", "SG", "SF", "PF", "C"))
paste0("Currently there are ",count(player_chi), " players in Chicago Bulls roaster.")

temp_index <- grep(max(player_chi$salary), player_chi$salary)
max_name <- player_chi[temp_index,]$player_name
max_salary <- player_chi[temp_index,]$salary
max_pos <- player_chi[temp_index,]$Pos
paste0("The most expensive player on the roaster is ", max_name, " with a salary of ", max_salary, ". His position is ", max_pos, ".")

temp_index <- grep(max(player_chi$MP), player_chi$MP)
max_time_name <- player_chi[temp_index,]$player_name
paste0("The player with the most minutes played is ", max_time_name, ".")

```

#### Relationships between variables

This section will explore the relationship between the variables chose and explained in the introduction for each position. It shall help to identify potential causal relationships between variables, to develop better models and make better predictions.

-   Point Guard

    Assists, 3-point field goal percentage on

```{r}
# 
```

-   Shooting Guard

```{r}

```

-   Small Forward

```{r}

```

-   Power Forward

```{r}

```

-   Center

```{r}

```

## 4. Data modelling and results

This section may include but is not limited to:

a)  data modelling (e.g. creating a linear regression)

b)  assumption checking

c)  model output and interpretation of your model

\

## 5. Player recommendations

**This section will be the key part that is presented to the general manager**. Here you should present your recommendations for the best five starting players, but also think about what other important information they would want to know, and how it is best to present that information to them.  

## 6. Summary

Provide a brief summary which describes the key points and findings from your project. It will also be important to acknowledge any limitations of your model and overall approach to answering the question asked of you by the general manager.

\

## 7. Reference list

1.  Haefner J. 7 ways to make a better point guard [Internet]. 2011 [cited 2023 May 7]. Available from: <https://www.usab.com/youth/news/2011/06/7ways-to-make-a-better-point-guard.aspx#:~:text=Point%20guard%20is%20perhaps%20the,against%20the%20opposing%20point%20guard.>

2.  The ultimate guide to playing small forward [Internet]. 2015 [cited 2023 May 8]. Available from: <https://www.usab.com/youth/news/2011/06/the-ultimate-guide-to-playing-small-forward.aspx>

3.  The ultimate guide to playing power forward [Internet]. 2015 [cited 2023 May 8]. Available from: <https://www.usab.com/youth/news/2011/06/the-ultimate-guide-to-playing-power-forward.aspx>

4.  How many players on a basketball team? (roster size) [Internet]. 2023 [cited 2023 May 8]. Available from: <https://www.gaimday.com/blog/players-basketball-team/>
